parental migration and adolescents educational performance

### 2023-02-24 analysis/Gu-thesis-script.Rmd
reference new studies

## Variables 
```{r Exam grade conversion}
d_cl <- d_cl |> mutate(
  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
```

@@

```{r Table for adjusted regression on exam grade}
table_adj_ttl <- models_adj_ttl |> msummary(
  stars =  stars,
  fmt = 2,
  title = title_cog,
  gof_omit = gof_omit,
  coef_rename =  coef_rename, 
  output = 'latex'
  )
```

@@

```{r Info for regression table with matching}
title_cog_matching <- 'Parental migration’s effect on children’s cognitive test scores, estimated with matching'
title_ttl_matching <- 'Parental migration’s effect on children’s academic exam scores, estimated with matching'
note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"
```

>>>>

## Variables 
```{r Exam grade conversion}
d_cl <- d_cl |> mutate(
  w1chn_100 = tr_chn/w2upchn*100, #raw exam score at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
```

@@

```{r Table for adjusted regression on exam grade}
table_adj_ttl <- models_adj_ttl |> msummary(
  stars =  stars,
  fmt = 2,
  title = title_ttl,
  gof_omit = gof_omit,
  coef_rename =  coef_rename, 
  output = 'latex'
  )
```

@@

```{r Info for regression table with matching}
title_cog_matching <- 'Parental migration’s effect on children’s cognitive test score, estimated with matching'
title_ttl_matching <- 'Parental migration’s effect on children’s academic exam score, estimated with matching'
note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"
```
